---
title: "Final Project Quarto Doc"
author: "Ginny Christman"
format: html
execute: 
  echo: false
---

## Data Description

This document features a historical dataset on the modern Olympic Games, including all the Games from Athens 1896 to Rio 2016. The dataset includes basic descriptive data on all athletes and medal results from their games.

## gtsummary table

```{r}
#| message: false
library(tidyverse)
library(here)
library(gtsummary)

athletes <- read_csv(here::here("Data","athlete_events.csv"))

table1 <- tbl_summary(
	athletes,
	by = Season, 
	include = c(Sex, Age, Height))|> 
  add_overall(last = TRUE)
```


```{r}
#| label: tbl-one
#| tbl-cap: "Descriptive Statistics on Athletes"
knitr::kable(table1)
```

## Regression results

```{r}
linear_model <- lm(Age ~ Height + Weight,
									 data = athletes)

regression <- tbl_regression(
	linear_model,
	intercept = TRUE)
```

```{r}
#| label: tbl-two
#| tbl-cap: "Linear Regression of height and weight on age"
knitr::kable(regression)
```

## Creating a Figure

```{r}
#| label: fig-hist
#| fig-cap: "Distribution of Athletes' Ages"
histogram <- hist(athletes$Age)

```
@fig-hist displays a histogram of the ages of the athletes and @tbl-one provides descriptive statistics on sex, age, and height.

```{r}
age <- inline_text(table1, variable = "Age", column = "stat_1")
```
There were `r nrow(athletes)` athletes in the dataset. 

The mean age of the athletes is (`r age`)
